---
title: "Seasonal behavior LMMs: Step 1- models"
output: html_document
date: "2025-05-23"
author: "Molly Caldwell"
---

```{r}
library(glmmTMB)
library(tidyverse)
library(Hmisc)
library(corrplot)
library(MuMIn)
library(flextable)
library(officer)
library(patchwork)
library(performance)
```

```{r setup}
setwd("~/OneDrive - University of Wyoming/Documents/USGS_AK_Caribou/")
```

# Load and prep data
2 sets of data and analyses for early summer (1 June - 15 July) and late summer (16 July - 31 August)

```{r}
# Early / late summer forage conditions data
res_cond_early <- readRDS("./Code_Output/early_forage_per_herdUDs.rds")
res_cond_late <- readRDS("./Code_Output/late_forage_per_herdUDs.rds")

# Early / late summer insect conditions data
ins_cond_early <- readRDS("./Code_Output/early_insect_per_herdUDs.rds")
ins_cond_late <- readRDS("./Code_Output/late_insect_per_herdUDs.rds")

# Early / late summer behaviors data
early_beh <- readRDS("./Code_Output/early_behaviors.rds")
late_beh <- readRDS("./Code_Output/late_behaviors.rds")
  
```

```{r}
# add year and animal id to behavior data
early_beh <- early_beh %>% 
  mutate(yr = as.numeric(str_split_i(animal_yr, "_", 2)),
         animal_id = str_split_i(animal_yr, "_", 1))

late_beh <- late_beh %>% 
  mutate(yr = as.numeric(str_split_i(animal_yr, "_", 2)),
         animal_id = str_split_i(animal_yr, "_", 1))

# combine forage, insect conditions and behavior datasets
early_beh <- left_join(early_beh, res_cond_early, by = c("yr" = "year"))
early_beh <- left_join(early_beh, ins_cond_early, by = c("yr" = "year"))


late_beh <- left_join(late_beh, res_cond_late, by = c("yr" = "year"))
late_beh <- left_join(late_beh, ins_cond_late, by = c("yr" = "year"))

```

```{r}
# scale and center forage and insect conditions
cond_vars <- c("avg_biom_herd",  "avg_dn_herd",
                 "avg_de_herd", 
               "avg_mosq_herd", 
               "avg_fly_herd")

early_beh <- early_beh %>% 
  mutate_at(cond_vars[!cond_vars %in% c("avg_fly_herd", "sd_fly_herd")],
            ~(scale(as.numeric(.), center = T, scale = T) %>% as.vector))


late_beh <- late_beh %>% 
  mutate_at(cond_vars[!cond_vars %in% c("avg_mosq_herd", "sd_mosq_herd")],
            ~(scale(as.numeric(.), center = T, scale = T) %>% as.vector))


```

```{r}
# early summer
# check correlation of conditions variables
rcorr(as.matrix(early_beh %>% 
                  select(all_of(cond_vars[!cond_vars %in% c("avg_fly_herd",
                                                            "sd_fly_herd")]))) )

# correlation plot
early_beh_corr = cor(early_beh %>% 
                       select(all_of(cond_vars[!cond_vars %in% c("avg_fly_herd",
                                                                 "sd_fly_herd")])) %>% 
        rename(forage_biomass = avg_biom_herd,
               dig_nitrogen = avg_dn_herd,
               dig_energy = avg_de_herd,
               mosq_index = avg_mosq_herd))
corrplot(early_beh_corr, method = 'number') 



# late summer
# check correlation of conditions variables
rcorr(as.matrix(late_beh %>% 
                  select(all_of(cond_vars[!cond_vars %in% c("avg_mosq_herd",
                                                            "sd_mosq_herd")]))))



# correlation plot
late_beh_corr = cor(late_beh %>% 
                       select(all_of(cond_vars[!cond_vars %in% c("avg_mosq_herd",
                                                                 "sd_mosq_herd")])) %>%  
                     rename(forage_biomass = avg_biom_herd,
               dig_nitrogen = avg_dn_herd,
               dig_energy = avg_de_herd,
               fly_index = avg_fly_herd) )
corrplot(late_beh_corr, method = 'number') 



```

```{r}
# save datasets used in models
saveRDS(early_beh, "./Code_Output/early_beh_LMM_data.rds")

saveRDS(late_beh, "./Code_Output/late_beh_LMM_data.rds")
```

# Early summer linear mixed models
## Early summer behaviors 
Model: behavior metric ~ predictors + (1|animal_id)
predictors include early summer herd range average biomass and digestible nitrogen and mosquito indices

Behavior metrics (individual-level):
Average daily distance
Average daily sinuosity
Average use of forage biomass
Average use of digestible nitogen & energy
Early summer home range area
Early summer home range x & y centroids
Resource hypervolume volume
Movement hypervolume volume


```{r}
# pull out behavior metrics (response variables)
beh_metrics <- c("avg_dist_m", "avg_sinuosity", "avg_biom", "avg_dn",
                 "avg_de", "HR_area_km2", "centroid_x", "centroid_y",
                 "resource_vol", "move_vol")


# run LMM per behavior metric
early_beh_models_S1 <- vector(mode = "list", length = length(beh_metrics))

for(i in 1:length(beh_metrics)){
  print(i)
  
    # model formula
    mod_form1 <- formula(paste(beh_metrics[[i]],
                            " ~ (1 | animal_id) + avg_biom_herd + avg_mosq_herd"))
    
     mod_form2 <- formula(paste(beh_metrics[[i]],
                            " ~ (1 | animal_id) + avg_dn_herd + avg_mosq_herd"))
     
     mod_form3 <- formula(paste(beh_metrics[[i]],
                            " ~ (1 | animal_id)"))
    
    # save LMM to list
  early_beh_models_S1[[i]][["Forage biomass"]] <- glmmTMB(mod_form1,
                                 family = gaussian(link = "identity"),
                                 data = early_beh)
  
  early_beh_models_S1[[i]][["Dig. nitrogen"]] <- glmmTMB(mod_form2,
                                 family = gaussian(link = "identity"),
                                 data = early_beh)
  
  early_beh_models_S1[[i]][["Null"]] <- glmmTMB(mod_form3,
                                 family = gaussian(link = "identity"),
                                 data = early_beh)
  
}

names(early_beh_models_S1) <- beh_metrics

```

```{r}
# AIC table
aic_df_S1 <- list()

for(i in 1:length(early_beh_models_S1)){
 
  # Generate AIC table per model set (per behavior metric)
  aic_table <- MuMIn::model.sel(early_beh_models_S1[[i]])
  
  # Add model names and set identifiers
  aic_df_S1[[i]] <- as.data.frame(aic_table) %>%
    tibble::rownames_to_column("model") %>%
    mutate(model_set = names(early_beh_models_S1)[[i]],
           .before = everything())
  

}

aic_df_S1 <- bind_rows(aic_df_S1)

```

```{r}
# output word docx AIC tables
## first, subset to variables of interest
aic_df_S1 <- aic_df_S1 %>% 
  select(model_set, model, df, logLik, AICc, delta, weight)

## then, round values
aic_df_S1 <- aic_df_S1 %>%
  mutate(across(where(is.numeric), ~round(.x, 3)))

# format it as a flextable
ft <- flextable(aic_df_S1)

# autofit column widths
ft <- autofit(ft)

# create a Word document and add the table
doc <- read_docx() %>%
  body_add_par("early behavior AIC", style = "heading 1") %>%
  body_add_flextable(ft)

# save the Word document
print(doc, target = "./Code_Output/early_behavior_AIC_S1.docx")
```

```{r}
# pull models with AIC > NULL
top_models <- vector(mode = "list", length = length(early_beh_models_S1))

for(i in 1:length(early_beh_models_S1)){
  print(i)
  set <- names(early_beh_models_S1)[[i]] # pull response set
  
  delta_NULL <- aic_df_S1 %>% 
    filter(model_set == set & model == "Null")
    
top_aic_mod <- aic_df_S1 %>% 
    filter(model_set == set & delta < delta_NULL$delta[1]) 

# pull model
  top_models[[i]] <- early_beh_models_S1[[set]][top_aic_mod$model]
}

names(top_models) <- names(early_beh_models_S1)

# remove empty list objects (responses with no significant predictors)
top_models <- top_models[sapply(top_models, length) > 0]

# save top models
saveRDS(top_models, "./Code_Output/early_behavior_LMMs.rds")
```


# Late summer linear mixed models
## Late summer behaviors 
Model: behavior metric ~ predictors + (1|animal_id)
predictors include late summer herd range average biomass, average and SD DE, average and SD fly indices

Behavior metrics (individual-level):
Average daily distance
Average daily sinuosity
Average use of forage biomass
Average use of digestible nitogen & energy
late summer home range area
late summer home range x & y centroids
Resource hypervolume volume
Movement hypervolume volume


```{r}
# pull out behavior metrics (response variables)
beh_metrics <- c("avg_dist_m", "avg_sinuosity", "avg_biom", "avg_dn",
                 "avg_de", "HR_area_km2", "centroid_x", "centroid_y",
                 "resource_vol", "move_vol")


# run LMM per behavior metric
late_beh_models_S1 <- vector(mode = "list", length = length(beh_metrics))

for(i in 1:length(beh_metrics)){
  print(i)
  
    # model formula
    mod_form1 <- formula(paste(beh_metrics[[i]],
                            " ~ (1 | animal_id) + avg_biom_herd + avg_fly_herd"))
    
     mod_form2 <- formula(paste(beh_metrics[[i]],
                            " ~ (1 | animal_id) + avg_de_herd + avg_fly_herd"))
     
     mod_form3 <- formula(paste(beh_metrics[[i]],
                            " ~ (1 | animal_id)"))
    
    # save LMM to list
  late_beh_models_S1[[i]][["Forage biomass"]] <- glmmTMB(mod_form1,
                                 family = gaussian(link = "identity"),
                                 data = late_beh)
  
  late_beh_models_S1[[i]][["Dig. energy"]] <- glmmTMB(mod_form2,
                                 family = gaussian(link = "identity"),
                                 data = late_beh)
  
  late_beh_models_S1[[i]][["Null"]] <- glmmTMB(mod_form3,
                                 family = gaussian(link = "identity"),
                                 data = late_beh)
  
}

names(late_beh_models_S1) <- beh_metrics

```

```{r}
# AIC table
aic_df_S1 <- list()

for(i in 1:length(late_beh_models_S1)){
 
  # Generate AIC table per model set (per behavior metric)
  aic_table <- MuMIn::model.sel(late_beh_models_S1[[i]])
  
  # Add model names and set identifiers
  aic_df_S1[[i]] <- as.data.frame(aic_table) %>%
    tibble::rownames_to_column("model") %>%
    mutate(model_set = names(late_beh_models_S1)[[i]],
           .before = everything())
  

}

aic_df_S1 <- bind_rows(aic_df_S1)

```

```{r}
# output word docx AIC tables
## first, subset to variables of interest
aic_df_S1 <- aic_df_S1 %>% 
  select(model_set, model, df, logLik, AICc, delta, weight)

## then, round values
aic_df_S1 <- aic_df_S1 %>%
  mutate(across(where(is.numeric), ~round(.x, 3)))

# format it as a flextable
ft <- flextable(aic_df_S1)

# autofit column widths
ft <- autofit(ft)

# create a Word document and add the table
doc <- read_docx() %>%
  body_add_par("late behavior AIC", style = "heading 1") %>%
  body_add_flextable(ft)

# save the Word document
print(doc, target = "./Code_Output/late_behavior_AIC_S1.docx")
```

```{r}
# pull models with AIC > NULL
top_models <- vector(mode = "list", length = length(late_beh_models_S1))

for(i in 1:length(late_beh_models_S1)){
  print(i)
  set <- names(late_beh_models_S1)[[i]] # pull response set
  
  delta_NULL <- aic_df_S1 %>% 
    filter(model_set == set & model == "Null")
    
top_aic_mod <- aic_df_S1 %>% 
    filter(model_set == set & delta < delta_NULL$delta[1]) 

# pull model
  top_models[[i]] <- late_beh_models_S1[[set]][top_aic_mod$model]
}

names(top_models) <- names(late_beh_models_S1)

# remove empty list objects (responses with no significant predictors)
top_models <- top_models[sapply(top_models, length) > 0]

# save top models
saveRDS(top_models, "./Code_Output/late_behavior_LMMs.rds")
```
